The Astropy Project

### 2017-11-24 main.tex
Edits to phrasing in 'support' paragraph.

@@

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of the \astropypkg.  Development of the \astropypkg is supported
by individuals who work on \astropy project in their own personal
time, by individuals or groups to work on \astropy as
part of a research project, or contributions from institutions that allocate
people to work on \astropy.
A list of organizations that have contributed to \astropy in this manner
can be found in the Acknowledgements.
Different funding models have been proposed for support of \astropy in the future
(e.g., \cite{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions
(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
open source scientific computing.},
which, has so far, covered the direct costs incurred by the \astropy project.

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
provides a full log of changes \footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation \footnote{\url{http://docs.astropy.org/en/stable/}}.
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

@@

\astropy provides a package template --- as a separate \github repository,
\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-template/}}
--- that aims to simplify setting up packaging, testing, and
documentation builds for developers of affiliated packages or
\astropypkg-dependent packages.
Any \python package can make use of this ready-to-go package layout, setup,
installation, and \package{Sphinx} documentation build infrastructure that was
originally developed for the \astropypkg core package and affiliated packages
maintained by the \astropy project.
The package template also provides a testing framework, template configurations
for continuous integration services, and \package{Cython} build support.

>>>>

% Words that should not be hyphenated
\hyphenation{NumFOCUS}

@@

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of \astropypkg.  Development of the software, all supporting materials, and community support is provided
by individuals who work on the \astropy project in their own personal
time, by individuals or groups contributing to \astropy as
part of a research project, or contributions from institutions that allocate
people to work on \astropy.
A list of organizations that have contributed to \astropy in this manner
can be found in the Acknowledgements.
Different funding models have been proposed for support of \astropy
(e.g., \cite{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions
from institutions or individuals through the NumFOCUS\footnote{NumFOCUS
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
open source scientific computing.} organization. NumFOCUS has to date covered the direct costs incurred by the \astropy project.

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

@@

\astropy provides a package template --- as a separate \github repository,
\package{astropy/package-template}\footnote{\url{https://github.com/astropy/package-t
emplate/}} --- that aims to simplify setting up packaging, testing, and
documentation builds for developers of affiliated packages or
\astropypkg-dependent packages.
Any \python package can make use of this ready-to-go package layout, setup,
installation, and \package{Sphinx} documentation build infrastructure that was
originally developed for the \astropypkg core package and affiliated packages
maintained by the \astropy project.
The package template also provides a testing framework, template configurations
for continuous integration services, and \package{Cython} build support.
